%------------------------------------
%	CV design by Andrew Q. Philips
%	10/26/18
%------------------------------------

\documentclass{article}

% FONT ------------
\usepackage[utf8]{inputenc}
\usepackage{helvet}

% DOCUMENT LAYOUT -----------
\usepackage{geometry} 
\geometry{a4paper, textwidth=6.5in, textheight=9.05in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}
\usepackage{comment}


% HEADINGS
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\rmfamily\mdseries\Large} 
\subsectionfont{\rmfamily\mdseries\scshape\normalsize} 
\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize} 
\usepackage{fancyhdr}
\pagestyle{fancy}
\rhead{\textbf{Poli T.\ Cal}}
\renewcommand{\headrulewidth}{0mm}% no header line please!
\AtBeginDocument{\thispagestyle{empty}} % no header on pg. 1


% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage{xcolor} % to define color
\definecolor{dkblue}{RGB}{1,0,98} % dk blue link color
\usepackage[bookmarks,
  	colorlinks,
   	breaklinks,
    pdftitle={Poli T Cal CV},
    pdfauthor={Poli T Cal}]{hyperref}  
\hypersetup{linkcolor=blue,
	citecolor=blue,
	filecolor=black,
	urlcolor=dkblue} 
	

% DOCUMENT ------------------------------------------
\begin{document}	

{\LARGE Poli T.\ Cal}			% Name
\vskip 1.4em

\begin{minipage}[t]{.5\textwidth}

Department of Political Science\\	% Address
University of Colorado Boulder\\ 
UCB 333, Boulder, CO 80309-0333


% Email and website
\end{minipage}
\begin{minipage}[t]{.5\textwidth}
\begin{flushright}
\href{mailto:polit.cal@colorado.edu}{polit.cal@colorado.edu}\\
 \href{http://www.politcal.com/}{www.politcal.com}\\
\end{flushright}
\end{minipage}


%\subsection*{\textbf{ACADEMIC APPOINTMENTS}}


\subsection*{\textbf{EDUCATION}}
Graduate Student, Department of Political Science, University of Colorado Boulder. 2015-present.

Concentrations: American Politics

Dissertation: ``Are the parties polarized?"

\vskip .25cm
\textit{BA}, Political Science, University of Cool. 2014.



\subsection*{\textbf{PUBLICATIONS}}

\noindent

Cal, Poli T. 2018. ``The parties are polarized'' \emph{Political Journal} 13(1) 250-280. 
\vskip .25cm
Cal, Poli T. 2016. ``Did Nixon cause Watergate?''  \emph{Political Journal}. 13(1) 250-280.


\subsection*{\textbf{WORKING PAPERS}}
\noindent
Cal, Poli T.  ``On Thomas Jefferson'' 
\vskip .25cm
Cal, Poli T. and Comp A. Rative ``Are Democrats more likely to own dogs?''  


\subsection*{\textbf{RESEARCH INTERESTS}}
Substantive: American politics, methodology, politics of dogs


\subsection*{\textbf{TEACHING INTERESTS}}
American, institutions, political behavior

\subsection*{\textbf{TECHNICAL SKILLS}}
Stata, \texttt{R}, \LaTeX


\subsection*{\textbf{FUNDING AND RESEARCH AWARDS}}
 Prestigious Grant 1. 2016
\vskip .25cm
Prestigious Grant 2. 2015


\subsection*{\textbf{RESEARCH EXPERIENCE}}
 Graduate Research Assistant for Professor X, CU Boulder, 2012-present.
\vskip .25cm
 Graduate Research Assistant for Professor Y, CU Boulder, 2015-present.


\subsection*{\textbf{TEACHING EXPERIENCE}}
Instructor, Political Behavior, CU Boulder, Spring 2016
\vskip .25cm
Teaching Assistant, Political Behavior, CU Boulder, Fall 2015
\vskip .25cm
Teaching Assistant, Political Theory, CU Boulder, Fall 2015


\subsection*{\textbf{RECENT CONFERENCE PRESENTATIONS}}
``The parties are polarized'' Presented at the Annual Meeting of the American Political Science Association. 2017
\vskip .15em
``The parties are polarized'' Presented at the Annual Meeting of the Midwest Political Science Association. 2016


\subsection*{\textbf{PROFESSIONAL MEMBERSHIP AND SERVICE}}
 Reviewer, {\it Journal of This, Journal of That, Journal of Other Things}.
 \vskip .25cm
 Member, Political Science Association\vskip .25cm


\subsection*{\textbf{REFERENCES}}
\begin{minipage}[t]{.5\textwidth}
{\centering

\textbf{X}\\
Professor\\
Department of Political Science\\
University of the Pacific\\
Address, CA \\
\href{mailto:professorx@up.edu}{professorx@up.edu}\\

\vspace{10mm}
\textbf{Y}\\
Professor\\
Department of Political Science\\
University of the Pacific\\
Address, CA \\
\href{mailto:professorx@up.edu}{professorx@up.edu}\\

}
\end{minipage}
\begin{minipage}[t]{.5\textwidth}{\centering

\textbf{M}\\
Professor\\
Department of Political Science\\
University of the South\\
Address, MS \\
\href{mailto:professorx@us.edu}{professorx@us.edu}\\

\vspace{10mm}
\textbf{Z}\\
Professor\\
Department of Political Science\\
University of the Atlantic\\
Address, NJ \\
\href{mailto:professorx@ua.edu}{professorx@ua.edu}\\
}

\end{minipage}

\vfill{}

\begin{center}
{\scriptsize  Last updated: \today \\
% ---- FILL IN THE FULL URL TO YOUR CV HERE
 \href{www.politcal.com/CV}{www.politcal.com/CV}}
\end{center}

\end{document}